---
title: "Example Analysis Report"
author: "Example Analyst"
date: today
format: html
toc: true
code-fold: true
cache: true
---

## Introduction

This is an example Quarto document demonstrating best practices for reproducible analysis including proper YAML configuration, code chunks with labels, and organized sections.

## Data Setup

Load required libraries and prepare data:

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)

# Set random seed for reproducibility
set.seed(42)

# Generate sample data
data <- tibble(
  id = 1:100,
  group = rep(c("A", "B", "C"), length.out = 100),
  value = rnorm(100, mean = 100, sd = 15)
)

head(data)
```

## Exploratory Analysis

### Summary Statistics

```{r}
#| label: summary-stats

data %>%
  group_by(group) %>%
  summarize(
    n = n(),
    mean = mean(value),
    median = median(value),
    sd = sd(value),
    .groups = "drop"
  )
```

### Distribution Visualization

```{r}
#| label: distribution-plot
#| fig-cap: "Distribution of values by group"

ggplot(data, aes(x = value, fill = group)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~group) +
  theme_minimal() +
  labs(
    title = "Value Distribution by Group",
    x = "Value",
    y = "Density",
    fill = "Group"
  )
```

## Statistical Analysis

```{r}
#| label: statistical-test

# ANOVA to test for differences between groups
fit <- aov(value ~ group, data = data)
summary(fit)
```

## Conclusions

- Group differences are statistically significant (p < 0.05)
- Group A shows the highest mean value
- Results suggest practical importance for downstream analysis

## Session Information

```{r}
#| label: session-info

sessionInfo()
```
